On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-11-19 paper.tex
update delay 1

\section{Case of $\delta = 1$}
\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \fill (0,0) circle[radius = 0.1];
      \fill (1.5,0) circle[radius = 0.1];
      \fill (3,0) circle[radius = 0.1];
      \fill (4.5,0) circle[radius = 0.1];
      \fill (6,0) circle[radius = 0.1];

@@

If a bead is stabilized through a tunnel section, then it can provide some bonds. Let us consider bonds of $C_i$. $C_i$ is represented $C = (W,P,H)$ where $|W| = i + n$ $C_i$ contains $\alpha \cdot (i + n) - 2|H|$ bonds because $C_i$ consists of $i + n$ beads and a bead has just $\alpha$ bonds and then $2 |H|$ of the those bonds are already used. However, even if a bead has an available bond, $w[j]$ $(j > i)$ might not be able to use this bond because the bond has possibility that it is blocked by transcripts $w[i+1..j-1]$. Number of $binding\ capabilities$ does not contain that case so that it is at most $\alpha \cdot (i + n) - 2|H|$.

\begin{definition}[binding capability]
We say that $p$ is $reachable$ if there exists directed path $P^\prime$ from $q$ to $p$ such that the path of $P^\prime$ does not cross the path of $P$ where $q_0$ is a bead which is latest stabilized, and $q_m$ is a reachable point. Let $B_i$ be $( \{ (h, i) | {}^\forall h < i \} \cup \{ (i, j) | {}^\forall j > i \}) \cap H$. Moreover, let $R_i$ be a set of inside $\hexagon_{w_i}^1$ that are free and reachable.
 We represent the number of binding capabilities of a conformation $C_j$ as $\#bc(C_j)$. $\#bc(C_j)$ is defined by $\sum^{j}_{k=-n+1} \min \{ |B_k|, |R_k|  \}$.
\end{definition}

@@

\begin{theorem}[Tunnel Troll Theorem]
Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$. If there is a part of transcript $w[i..j+1] = bttt...tb$, then $\#bc(C_i)$ is more than $\#bc(C_j)$.
\end{theorem}

@@

>>>>

\section{Case of $\delta = 1$}

%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%
%Kohei
%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \fill (0,0) circle[radius = 0.1];
      \fill (1.5,0) circle[radius = 0.1];
      \fill (3,0) circle[radius = 0.1];
      \fill (4.5,0) circle[radius = 0.1];
      \fill (6,0) circle[radius = 0.1];

@@

%If a bead is stabilized through a tunnel section, then it can provide some bonds. Let us consider bonds of $C_i$. $C_i$ is represented $C = (W,P,H)$ where $|W| = i + n$ $C_i$ contains $\alpha \cdot (i + n) - 2|H|$ bonds because $C_i$ consists of $i + n$ beads and a bead has just $\alpha$ bonds and then $2 |H|$ of the those bonds are already used. However, even if a bead has an available bond, $w[j]$ $(j > i)$ might not be able to use this bond because the bond has possibility that it is blocked by transcripts $w[i+1..j-1]$. Number of $binding\ capabilities$ does not contain that case so that it is at most $\alpha \cdot (i + n) - 2|H|$.

We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$. We define $binding\ capability$ with reachable.

\begin{definition}[binding capability]
Let $B_i$ be $( \{ (h, i) | {}^\forall h < i \} \cup \{ (i, j) | {}^\forall j > i \}) \cap H$. Moreover, let $R_i$ be a set of neighbors of $w[i]$ that are free and reachable from $C_j$ where $C_j$ is a conformation which stabilized until $w[j]$.
 We represent the number of binding capabilities of a conformation $C_j$ as $\#bc(C_j)$. $\#bc(C_j)$ is defined by $\sum^{j}_{k=-n+1} \min \{ |B_k|, |R_k|  \}$.
\end{definition}

@@

\begin{theorem}[Tunnel Troll Theorem]
Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$. If there are indices $i$ and $j$ such that $S[i..j+1] = bt^{j-i}b$, then $\#bc(C_i)$ > $\#bc(C_j)$.
\end{theorem}

@@

%end of d = 1
%//////////////////////////////////////////////////////%
%//////////////////////////////////////////////////////%
